Code used to generate paper results : Database comparison and CT characteristics

### 2024-06-11 Paper_code-CT_analysis.Rmd
Minor change

  h <- Heatmap(mat[gene_type$gene, rownames(df_col), drop = FALSE],
               name = "logTPM",
               row_split = factor(gene_type$Regulation, 
                                  levels = c("Methylation", "Not methylation")),
               row_title_gp = gpar(col = Regulation_colors, fontsize = 6),
               border = TRUE,
               border_gp = gpar(lwd = 0.5),
               column_title = "Expression in cells treated with 5-Aza",
               column_title_gp = gpar(fontsize = 6),
               column_split = factor(df_col$cell),
               col = colorRamp2(seq(scale_lims[1], scale_lims[2], length = 11),
                                legend_colors),
               cluster_rows = TRUE,
               show_row_dend = FALSE,
               show_row_names = FALSE,
               clustering_method_rows = "ward.D",
               show_column_names = FALSE,
               cluster_columns = FALSE,
               row_names_gp = gpar(fontsize = row_fontsize),
               top_annotation = c(column_ha_cell, column_ha_treatment),
               # right_annotation = c(row_ha_ts,
               #                      #row_ha_regulation,
               #                      row_ha_chr,
               #                      gap = unit(1, "mm")),
               heatmap_width = unit(6, "cm"),
               heatmap_height = unit(10, "cm"),
               use_raster = TRUE,
               raster_device = "CairoPNG",
               raster_quality = 10,
               heatmap_legend_param = legends_param)

>>>>

  h <- Heatmap(mat[gene_type$gene, rownames(df_col), drop = FALSE],
               name = "logCounts",
               row_split = factor(gene_type$Regulation, 
                                  levels = c("Methylation", "Not methylation")),
               row_title_gp = gpar(col = Regulation_colors, fontsize = 6),
               border = TRUE,
               border_gp = gpar(lwd = 0.5),
               column_title = "Expression in cells treated with 5-Aza",
               column_title_gp = gpar(fontsize = 6),
               column_split = factor(df_col$cell),
               col = colorRamp2(seq(scale_lims[1], scale_lims[2], length = 11),
                                legend_colors),
               cluster_rows = TRUE,
               show_row_dend = FALSE,
               show_row_names = FALSE,
               clustering_method_rows = "ward.D",
               show_column_names = FALSE,
               cluster_columns = FALSE,
               row_names_gp = gpar(fontsize = row_fontsize),
               top_annotation = c(column_ha_cell, column_ha_treatment),
               # right_annotation = c(row_ha_ts,
               #                      #row_ha_regulation,
               #                      row_ha_chr,
               #                      gap = unit(1, "mm")),
               heatmap_width = unit(6, "cm"),
               heatmap_height = unit(10, "cm"),
               use_raster = TRUE,
               raster_device = "CairoPNG",
               raster_quality = 10,
               heatmap_legend_param = legends_param)
